A Decision Procedure for String Constraints with String-Integer Conversion and Flat Regular Constraints

### 2021-05-18 FMCAD2021/6_impl_exp.tex
add trau result

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% Merge bound and unbound 
\begin{table*}[]
    \label{table:arithmetic}
    \caption{Results of Z3, CVC4 and $\paexp$-Solver on arithmetic benchmark}
    \centering
    \begin{tabular}{cc|cc|cc|cc}
        \multicolumn{1}{l}{} &  & \multicolumn{2}{c|}{Z3} & \multicolumn{2}{c|}{CVC4} & \multicolumn{2}{c}{MySolver} \\
        \multicolumn{1}{l}{} &  & number & avg & number & avg & number & avg \\ \hline
        \multirow{4}{*}{2-3-3-4} & SAT & 56 & 0.4 & 42 & 2.3 & 64 & 0.4 \\
         & UNSAT & 69 & \textless{}0.1 & 72 & \textless{}0.1 & 89 & \textless{}0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 47 & 9.5 \\
         & TIMEOUT & 75 &  & 86 &  & 0 &  \\ \hline
        \multirow{4}{*}{3-4-4-5} & SAT & 33 & 1.4 & 25 & 2.9 & 52 & 3.3 \\
         & UNSAT & 59 & \textless{}0.1 & 60 & \textless{}0.1 & 88 & \textless{}0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 1 & 54.0 \\
         & TIMEOUT & 108 &  & 115 &  & 59 &  \\ \hline
        \multirow{4}{*}{4-5-5-6} & SAT & 35 & 1.8 & 19 & 6.6 & 47 & 22.4 \\
         & UNSAT & 36 & 0.3 & 39 & 0.4 & 72 & 0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 0 &  \\
         & TIMEOUT & 129 &  & 142 &  & 81 & 
        \end{tabular}
\end{table*}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table*}[]
    \label{table:string}
    \caption{Results of Z3, CVC4 and $\paexp$-Solver on string hash function benchmark}
    \begin{tabular}{c|c|ccc|ccc|ccc}
                                                       &     & \multicolumn{3}{c|}{Z3} & \multicolumn{3}{c|}{CVC4} & \multicolumn{3}{c}{MySolver}       \\
    PATTERN                                            & $\ell_{10}(m_1)$   & SAT  & UNSAT  & TIMEOUT & SAT   & UNSAT  & TIMEOUT  & SAT & UNSAT & TIMEOUT              \\ \hline
    \multirow{5}{*}{12345(a)*(b)*}                     & 2   & 5    &        & 20      & 23    &        & 2        & 24  & 1     & 0                    \\
                                                       & 3   & 0    &        & 25      & 4     &        & 21       & 10  & 14    & 1                    \\
                                                       & 4   & 0    &        & 25      & 1     &        & 24       & 2   & 22    & 1                    \\
                                                       & 5   & 0    &        & 25      & 1     &        & 24       & 1   & 23    & 1                    \\
                                                       & total & 5    &        & 95      & 29    &        & 71       & 37  & 60    & 3                    \\ \hline
    \multirow{5}{*}{12345(a)*(b)*6789}                 & 2   & 10   &        & 15      & 18    &        & 7        & 24  & 1     & 0                    \\
                                                       & 3   & 1    &        & 24      & 8     &        & 17       & 10  & 15    & 0                    \\
                                                       & 4   & 0    &        & 25      & 3     &        & 22       & 3   & 22    & 0                    \\
                                                       & 5   & 0    &        & 25      & 0     &        & 25       & 0   & 25    & 0                    \\
                                                       & total & 11   &        & 89      & 29    &        & 71       & 37  & 63    & 0                    \\ \hline
    \multirow{5}{*}{(a)*(b)*6789}                      & 2   & 14   &        & 11      & 23    &        & 2        & 22  & 3     & 0                    \\
                                                       & 3   & 4    &        & 21      & 6     & 1      & 18       & 15  & 10    & 0                    \\
                                                       & 4   & 0    &        & 25      & 1     &        & 24       & 3   & 22    & 0                    \\
                                                       & 5   & 0    &        & 25      & 0     &        & 25       & 1   & 24    & 0                    \\
                                                       & total & 18   &        & 82      & 30    & 1      & 69       & 41  & 59    & 0                    \\ \hline\hline
    \multirow{5}{*}{12345$(\Sigma_{num})^*$}     & 2   & 25   &        & 0       & 25    &        & 0        & 25  &       &                      \\
                                                       & 3   & 25   &        & 0       & 25    &        & 0        & 25  &       &                      \\
                                                       & 4   & 23   &        & 2       & 25    &        & 0        & 25  &       &                      \\
                                                       & 5   & 9    &        & 16      & 25    &        & 0        & 25  &       &                      \\
                                                       & total & 82   &        & 18      & 100   &        & 0        & 100 &       &                      \\ \hline
    \multirow{5}{*}{12345$(\Sigma_{num})^*$6789} & 2   & 25   &        & 0       & 15    &        & 10       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 3   & 23   &        & 2       & 1     &        & 24       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 4   & 9    &        & 16      & 1     &        & 24       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 5   & 3    &        & 22      & 0     &        & 25       & 25  &       &                      \\
                                                       & total & 60   &        & 40      & 17    &        & 83       & 100 &       &                      \\ \hline
    \multirow{5}{*}{$(\Sigma_{num})^*$6789}      & 2   & 25   &        & 0       & 19    &        & 6        & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 3   & 25   &        & 0       & 4     &        & 21       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 4   & 16   &        & 9       & 4     &        & 21       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & 5   & 2    &        & 23      & 0     &        & 25       & 25  &       & \multicolumn{1}{l}{} \\
                                                       & total & 68   &        & 32      & 27    &        & 73       & 100 &       &                     
    \end{tabular}
\end{table*}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% Merge bound and unbound 
\begin{table*}[]
    \label{table:arithmetic}
    \caption{Results of Z3, CVC4 and $\paexp$-Solver on arithmetic benchmark}
    \centering
    \begin{tabular}{cc|cc|cc|cc}
        \multicolumn{1}{l}{} &  & \multicolumn{2}{c|}{Z3} & \multicolumn{2}{c|}{CVC4} & \multicolumn{2}{c}{$\paexp$-solver} \\
        \multicolumn{1}{l}{} &  & number & avg & number & avg & number & avg \\ \hline
        \multirow{4}{*}{2-3-3-4} & SAT & 56 & 0.4 & 42 & 2.3 & 64 & 0.4 \\
         & UNSAT & 69 & \textless{}0.1 & 72 & \textless{}0.1 & 89 & \textless{}0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 47 & 9.5 \\
         & TIMEOUT & 75 &  & 86 &  & 0 &  \\ \hline
        \multirow{4}{*}{3-4-4-5} & SAT & 33 & 1.4 & 25 & 2.9 & 52 & 3.3 \\
         & UNSAT & 59 & \textless{}0.1 & 60 & \textless{}0.1 & 88 & \textless{}0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 1 & 54.0 \\
         & TIMEOUT & 108 &  & 115 &  & 59 &  \\ \hline
        \multirow{4}{*}{4-5-5-6} & SAT & 35 & 1.8 & 19 & 6.6 & 47 & 22.4 \\
         & UNSAT & 36 & 0.3 & 39 & 0.4 & 72 & 0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 0 &  \\
         & TIMEOUT & 129 &  & 142 &  & 81 & 
        \end{tabular}
\end{table*}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table*}[]
    \label{table:string}
    \caption{Results of Z3, CVC4 and $\paexp$-Solver on string hash function benchmark}
    \begin{tabular}{cc|ccc|ccc|ccc|ccc}
        &  & \multicolumn{3}{c|}{Z3} & \multicolumn{3}{c|}{CVC4} & \multicolumn{3}{c|}{Trau} & \multicolumn{3}{c}{$\paexp$-solver} \\
       PATTERN & k & SAT & UNSAT & FAIL & SAT & UNSAT & FAIL & SAT & UNSAT & FAIL & SAT & UNSAT & FAIL \\ \hline
       \multirow{5}{*}{$12345(a)^+(b)^+$} & 2 & 5 &  & 20 & 23 &  & 2 & 3 & 1 & 21 & 24 & 1 & 0 \\
        & 3 & 0 &  & 25 & 4 &  & 21 & 0 & 14 & 11 & 10 & 14 & 1 \\
        & 4 & 0 &  & 25 & 1 &  & 24 & 0 & 22 & 3 & 2 & 22 & 1 \\
        & 5 & 0 &  & 25 & 1 &  & 24 & 0 & 23 & 2 & 1 & 23 & 1 \\
        & all & 5 &  & 95 & 29 &  & 71 & 5 & 60 & 32 & 37 & 60 & 3 \\ \hline
       \multirow{5}{*}{$12345(a)^+(b)^+6789$} & 2 & 10 &  & 15 & 18 &  & 7 & 0 & 1 & 24 & 24 & 1 &  \\
        & 3 & 1 &  & 24 & 8 &  & 17 & 0 & 15 & 10 & 10 & 15 &  \\
        & 4 & 0 &  & 25 & 3 &  & 22 & 0 & 22 & 3 & 3 & 22 &  \\
        & 5 & 0 &  & 25 & 0 &  & 25 & 0 & 25 & 0 & 0 & 25 &  \\
        & all & 11 &  & 89 & 29 &  & 71 & 10 & 63 & 37 & 37 & 63 &  \\ \hline
       \multirow{5}{*}{$(a)^+(b)^+6789$} & 2 & 14 &  & 11 & 23 & 0 & 2 & 2 & 3 & 20 & 22 & 3 &  \\
        & 3 & 4 &  & 21 & 6 & 1 & 18 & 0 & 10 & 15 & 15 & 10 &  \\
        & 4 & 0 &  & 25 & 1 & 0 & 24 & 0 & 22 & 3 & 3 & 22 &  \\
        & 5 & 0 &  & 25 & 0 & 0 & 25 & 0 & 24 & 1 & 1 & 24 &  \\
        & all & 18 &  & 82 & 30 & 1 & 69 & 2 & 59 & 39 & 41 & 59 &  \\ \hline
       \multirow{5}{*}{$12345\Sigma^*$} & 2 & 25 &  & 0 & 25 &  & 0 & 25 &  & 0 & 25 &  &  \\
        & 3 & 25 &  & 0 & 25 &  & 0 & 2 &  & 23 & 25 &  &  \\
        & 4 & 23 &  & 2 & 25 &  & 0 & 1 &  & 24 & 25 &  &  \\
        & 5 & 9 &  & 16 & 25 &  & 0 & 0 &  & 25 & 25 &  &  \\
        & all & 82 &  & 18 & 100 &  & 0 & 28 &  & 72 & 100 &  &  \\ \hline
       \multirow{5}{*}{$12345\Sigma^*6789$} & 2 & 25 &  & 0 & 15 &  & 10 & 3 &  & 22 & 25 &  & \multicolumn{1}{l}{} \\
        & 3 & 23 &  & 2 & 1 &  & 24 & 0 &  & 25 & 25 &  & \multicolumn{1}{l}{} \\
        & 4 & 9 &  & 16 & 1 &  & 24 & 0 &  & 25 & 25 &  & \multicolumn{1}{l}{} \\
        & 5 & 3 &  & 22 & 0 &  & 25 & 0 &  & 25 & 25 &  &  \\
        & all & 60 &  & 40 & 17 &  & 83 & 3 &  & 97 & 100 &  &  \\ \hline
       \multirow{5}{*}{$\Sigma^*6789$} & 2 & 25 &  & 0 & 19 &  & 6 & 22 &  & 3 & 25 &  & \multicolumn{1}{l}{} \\
        & 3 & 25 &  & 0 & 4 &  & 21 & 2 &  & 24 & 25 &  & \multicolumn{1}{l}{} \\
        & 4 & 16 &  & 9 & 4 &  & 21 & 0 &  & 25 & 25 &  & \multicolumn{1}{l}{} \\
        & 5 & 2 &  & 23 & 0 &  & 25 & 0 &  & 25 & 25 &  & \multicolumn{1}{l}{} \\
        & all & 68 &  & 32 & 27 &  & 73 & 24 &  & 76 & 100 &  & 
       \end{tabular}
\end{table*}
